\documentclass[a4paper, 11pt]{scrartcl}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{url}

\title {Student Robotics 2014\\ Team Leader Agreement}
\author{Revision 1}
\date{\today}

\begin {document}
\maketitle

This is an agreement between the organisers of the Student Robotics
competition, and you the ``Team leader'' in charge of a team taking part
in the Student Robotics competition. The organisers of Student Robotics are
the current members of the committee, namely Sophia Maria, Rich Barlow,
Sam Phippen, Andy Cottrell, Jeremy Morse, and Rob Spanton.

\paragraph{}

Please read the agreement below, fill out the form at the end, and sign to
indicate your agreement. Please then return the signed Team Leader Agreement to:
\begin{quote}
	Student Robotics \\
	C/O Jeremy Morse \\
	B53 R4033 \\
	Dept of ECS \\
	University of Southampton \\
	SOUTHAMPTON \\
	SO17 1BJ
\end{quote}

For any questions about Student Robotics or this agreement, please email
\url{jmorse@studentrobotics.org}. In the event of an emergency or urgent
inquiry, please phone 07837210332.

\paragraph{}

The organisers will:

\begin{enumerate}
\item \textbf{The Kit}\\
\begin{enumerate}

\item Student Robotics will provide you with an electronics kit (``The Kit''),
the contents of which are catalogued in appendix A.

\item The Kit is on loan, and it must be returned at the end Competition,
unless you make mutually agreeable arrangements with Student Robotics for an
extended loan.

\item You take responsibility for the safety of the kit against theft and
damage.

\item When sent in the post or via courier, the Kit must be insured to the value
of at least \textsterling500.

\item Student Robotics may, at our discretion, chose to repair damage to the
Kit caused while operating it.

\item The documentation on how to operate the Kit is maintained on our website,
at \url{https://studentrobotics.org/docs}.
\end{enumerate}

\item \textbf{Events}
\begin{enumerate}

\item Student Robotics will organise a number of events through the year, as
listed below.

\item Student Robotics will provide suitable risk assessments in advance for all events.

\item Details of each event will be announced via email and on our website.

\item We will not provide transportation, accommodation, or meals,
to / from / or at any of these events. You must organize these yourself.

\item We will not provide any tools or equipment for building robots at these
events.

\item Student Robotics is not responsible for any tools or equipment that you
or your team bring to any of these events.

\item Kickstart

\begin{enumerate}
\item The Kickstart event will introduce the schedule of the Student Robotics
year.

\item The Kit will be issued to teams at Kickstart.

\item An explanation of how to operate the Kit will be given.

\item The Game will be introduced.
\end{enumerate}

\item Tech Days

\begin{enumerate}
\item Tech Days will be organized throughout the year as support sessions for
teams.

\item Teams are encouraged to attend Tech Days to meet other teams and share
ideas.

\item Our contributors will be present to provide advice on building the robot.
\end{enumerate}

\item The Competition
\begin{enumerate}

\item The Competition will be a two day event in April.

\item All participating teams must attend the competition.

\item Teams' robots will operate in an arena, playing the Game, in competition
with robots from other teams.

\item We will provide a desk, workspace, electricity, and internet connectivity
to allow you to to work on your robot at the Competition

\item XXX uuurrrggghhh

\end{enumerate}
\end{enumerate}

\item \textbf{The Website}
\begin{enumerate}

\item Student Robotics will maintain our website (\url{https://studentrobotics.org}).

\item The Website serves the latest documentation for the Kit.

\item The Website also serves the IDE, a web application for writing code for
your robot, and formatting it to run on your robot. (XXX -- copyright?
Sect 3.3 of the analysis / opinion?)

\item A forum is present on the website for competitors to communicate with
each other and share ideas.

\item We will provide website accounts to competitors for our forums and IDE. To
maintain these accounts, we store the following pieces of data:

\begin{itemize}
\item First name,
\item Last name,
\item Contact email address,
\item Team/School
\end{itemize}
We will not share any of this information with third parties, except when
printing participation certificates, when we will send a list of names to
our printers. The email address will only be used to send (infrequent) bulk
organization email to students, although in exceptional circumstances we
may email the student directly regarding something they've done on the
website.

\item The IDE and forums will be available for use by team leaders and competitors
from the Kickstart event until three weeks after the Competition Weekend.

\end{enumerate}

\item \textbf{Team Leader Responsibilities}
\begin{enumerate}

\item You must be an adult, who has the consent of the competitors parents, to
lead their team and be responsible for them.

\item Evidence of parental consent must be provided if requested by Student
Robotics.

\item It is your responsibility to supervise, or arrange suitable supervision,
for competitors in your team at all Student Robotics organised events.

\item Student Robotics is not liable for the actions of your competitors at
these events, nor competitors from other teams.

\item During the build period, you are responsible for the safety of the
competitors as they build their robot and operate the Kit. XXX fully disclaim
things like tools?

\end{enumerate}

\item \textbf{Withdrawal}
\begin{enumerate}

\item \textbf{Teams}: It is the responsibility of the Team Leader inform
Student Robotics (XXX via CONTACT-DETAIL?) if their team wishes to withdraw
from the Student Robotics Competition. This should be done as soon as possible,
and must be done before the Competition Weekend.

\item \textbf{Team members}: It is the responsibility of the Team Leader inform
Student Robotics (XXX via CONTACT-DETAIL?) if one of their team members
wishes to withdraw from the Student Robotics Competition. This should be
done as soon as possible, and must be done before the Competition Weekend.

\end{enumerate}

\item MCF?

\end{enumerate}

\appendix

\input{kit-return.tex}

\noindent
\textbf{Registration details and agreement.} \\
\doublespacing
\noindent
Your Name:\hrulefill\\
Your Email Address:\hrulefill\\
Your relationship with the competitors:\hrulefill\\
Your address:\hrulefill\\
\hbox{}\hrulefill\\
\hbox{}\hrulefill\\
(We will ship replacement kit and any other items to this address.)

\noindent
\dotfill\hfill

\noindent
I have read and agree to the above Team Leader Agreement\\
Signed:\hrulefill\\
Date:\hrulefill\\

\singlespacing


\end{document}
